High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-08-30 paper/main.tex
working on temporal decoding section

\section*{Methods}
Our general approach to comprises four general steps
(Fig.~\ref{fig:methods}).  First, we derive a kernel-based approach to
computing dynamic pairwise correlations in a $T$ (timepoints) by $K$
(features) multivariate timeseries, $\mathbf{X}_0$.  This yields a $T$
by $\mathcal{O}(K^2)$ matrix of dynamic correlations, $\mathbf{Y}_1$,
where each row comprises the upper triangle of the correlation matrix
at a single timepoint, reshaped into a row vector (this reshaped
vector is $(\frac{K^2 - K}{2})$-dimensional).  Second, we apply a
dimensionality reduction step to project the matrix of dynamic
correlations back onto a $K$-dimensional space.  This yields a $T$ by
$K$ matrix, $\mathbf{X}_1$, that reflects an approximation of the
dynamic correlations reflected in the original data.  Third, we use
repeated applications of the kernel-based dynamic correlation step to
$\mathbf{X}_n$ and the dimensionality reduction step to the resulting
$\mathbf{Y}_{n+1}$ to estimate high-order dynamnic correlations.  Each
application of these steps to a $T$ by $K$ time series $\mathbf{X}_n$
yields a $T$ by $K$ matrix, $\mathbf{X}_{n+1}$, that reflects the
dynamic correlations between the columns of $\mathbf{X}_n$.  In this
way, we refer to $n$ as the \textit{order} of the timeseries, where
$\mathbf{X}_0$ (order 0) denotes the original data and $\mathbf{X}_n$
denotes $n^\mathrm{th}$-order dynamic correlations between the columns
of $\mathbf{X}_0$.  Finally, we use a cross-validation--based decoding
approach to evaluate how well information contained in a given order
(or weighted mixture of orders) may be used to decode relevant
cognitive states.  If including a given $\mathbf{X}_n$ in the feature
set yields higher classification accuracy on held-out data, we
interpret this as evidence that the given cognitive states are
reflected in patterns of $n^\mathrm{th}$-order correlations.

@@

\subsubsection*{Functional neuroimaging data collected during story
  listening}
We examined an fMRI dataset collected by \cite{SimoEtal16} that the
authors have made publically available at
http://arks.princeton.edu/ark:/88435/dsp015d86p269k.  The dataset
comprises neuroimaging data collected as participants listened
to an audio recording of a story (intact condition; 36 participants),
listened to time scrambled recordings of the same story (17
participants in the paragraph-scrambled condition listened to the
paragraphs in a randomized order and 36 in the word-scrambled
condition listened to the words in a randomized order), or lay resting
with their eyes open in the scanner (rest condition; 36
participants).  Full neuroimaging details may be found in the original
paper~\citep{SimoEtal16}.

Following our prior related work, we used hierarchical topographic
factor analysis~\citep{MannEtal18} to derive a compact representation
of the data.  In brief, this approach approximates the timeseries of voxel
activations (44,415 voxels) using a much smaller number of radial
basis function nodes (in this case 700 nodes).  This provides a convenient
representation for examining full-brain network dynamics.  All of the
analyses we carried out on the neuroimaging dataset were performed in
this lower-dimensional space. \textbf{JRM STOPPED HERE}

\subsection*{Temporal decoding}
\subsubsection*{Forward inference, cross validation, and feature selection}
\subsubsection*{Identifying robust decoding results}
\subsubsection*{Reverse inference}

@@

To explore how higher-order structure varies with stimulus structure
and complexity, we used a previous neuroimaging dataset
~\cite{SimoEtal16}  in which participants listened to an audio recording of a story; 36 particpants listen to an intact version of the story, 17 participants listen to time-scrambled recordings of the same story where paragraphs were scrambled, 36 particpants listen to word-scrambled version and 36 participants lay in rest condition.

>>>>

\section*{Methods}
Our general approach to comprises four general steps
(Fig.~\ref{fig:methods}).  First, we derive a kernel-based approach to
computing dynamic pairwise correlations in a $T$ (timepoints) by $K$
(features) multivariate timeseries, $\mathbf{X}_0$.  This yields a $T$
by $\mathcal{O}(K^2)$ matrix of dynamic correlations, $\mathbf{Y}_1$,
where each row comprises the upper triangle of the correlation matrix
at a single timepoint, reshaped into a row vector (this reshaped
vector is $(\frac{K^2 - K}{2})$-dimensional).  Second, we apply a
dimensionality reduction step to project the matrix of dynamic
correlations back onto a $K$-dimensional space.  This yields a $T$ by
$K$ matrix, $\mathbf{X}_1$, that reflects an approximation of the
dynamic correlations reflected in the original data.  Third, we use
repeated applications of the kernel-based dynamic correlation step to
$\mathbf{X}_n$ and the dimensionality reduction step to the resulting
$\mathbf{Y}_{n+1}$ to estimate high-order dynamnic correlations.  Each
application of these steps to a $T$ by $K$ time series $\mathbf{X}_n$
yields a $T$ by $K$ matrix, $\mathbf{X}_{n+1}$, that reflects the
dynamic correlations between the columns of $\mathbf{X}_n$.  In this
way, we refer to $n$ as the \textit{order} of the timeseries, where
$\mathbf{X}_0$ (order 0) denotes the original data and $\mathbf{X}_n$
denotes $n^\mathrm{th}$-order dynamic correlations between the columns
of $\mathbf{X}_0$.  Finally, we use a cross-validation--based decoding
approach to evaluate how well information contained in a given order
(or weighted mixture of orders) may be used to decode relevant
cognitive states.  If including a given $\mathbf{X}_n$ in the feature
set yields higher classification accuracy on held-out data, we
interpret this as evidence that the given cognitive states are
reflected in patterns of $n^\mathrm{th}$-order correlations.  All of
the code used to produce the figures and results in this manuscript,
along with links to the corresponding datasets, may be found at
\href{https://github.com/ContextLab/timecorr-paper}{github.com/ContextLab/timecorr-paper}.  In addition, we have
released a Python toolbox for computing dynamic high-order
correlations in timeseries data; our toolbox may be found at
\href{https://timecorr.readthedocs.io/}{timecorr.readthedocs.io}. \textbf{JRM NOTE: CHECK LINK}

@@

\subsubsection*{Functional neuroimaging data collected during story
  listening}
We examined an fMRI dataset collected by \cite{SimoEtal16} that the
authors have made publically available at
\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.  The dataset
comprises neuroimaging data collected as participants listened
to an audio recording of a story (intact condition; 36 participants),
listened to time scrambled recordings of the same story (17
participants in the paragraph-scrambled condition listened to the
paragraphs in a randomized order and 36 in the word-scrambled
condition listened to the words in a randomized order), or lay resting
with their eyes open in the scanner (rest condition; 36
participants).  Full neuroimaging details may be found in the original
paper~\citep{SimoEtal16}.

Following our prior related work, we used hierarchical topographic
factor analysis~\citep{MannEtal18} to derive a compact representation
of the data.  In brief, this approach approximates the timeseries of
voxel activations (44,415 voxels) using a much smaller number of
radial basis function nodes (in this case 700 nodes).  This provides a
convenient representation for examining full-brain network dynamics.
All of the analyses we carried out on the neuroimaging dataset were
performed in this lower-dimensional space.  Code for carrying out
hierarchical topographic factor analyses on fMRI data may be found as
part of the BrainIAK toolbox~\citep{brainiak}, which may be downloaded
at \href{https://brainiak.org/}{brainiak.org}.

\subsection*{Temporal decoding}
We sought to identify neural patterns that reflected participants'
ongoing cognitive processing of incoming stimulus information.  As
reviewed by \cite{SimoEtal16}, one way of homing in on these
stimulus-driven neural patterns is to compare activity patterns across
individuals (e.g., using ISFC analyses).  In particular, neural
patterns will be similar across individuals, to the extent that the
neural patterns under consideration are stimulus driven, and to the
extent that the corresponding cognitive representations are reflected
in similar spatial patterns across people.  Following this logic, we
used an across-participants temporal decoding test developed by
\cite{MannEtal18} to assess the degree to which different neural
patterns reflected ongoing stimulus-driven cognitive processing across
people.  The approach entails using a subset of the data to train a
classifier to decode which stimulus timepoint (i.e., moment in the
story participants listened to).  We use decoding accuracy on held-out
data (from held-out participants) as a proxy for the extent to which
the inputted neural patterns reflected stimulus-driven cognitive
processing in a similar way across individuals.  \textbf{JRM STOPPED HERE}

\subsubsection*{Forward inference}

\subsubsection*{Cross validation}
\subsubsection*{Feature selection}
\subsubsection*{Identifying robust decoding results}
\subsubsection*{Reverse inference}

@@
